Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
Clarify

The algorithm performs a constraint-based search. We have a variable $D_v$ for each vertex $v$ in
the pattern graph, each of which has a domain containing one value for every vertex in the target
graph. The algorithm is bit-parallel: each $D_v$ is a bitset, and all graphs are stored as adjacency
matrices.

>>>>

The algorithm performs a constraint-based search. We have a set $D$ containing a variable $D_v$ for
each vertex $v$ in the pattern graph. Each variable has a domain containing one value for every
vertex in the target graph. The algorithm is bit-parallel: each $D_v$ is stored using bitset, and
all graphs are stored as adjacency matrices.
